Pipeline Performance Figure Generation

### 2023-06-28 TestingPipeline/Scripts/paper_figure_generation.Rmd
Figure 5 with three breaks.

pheatmap::pheatmap(prop_high_viruses,
                  annotation_row = ann_row,
                  annotation_col=ann_col,
                  annotation_colors = ann_colors,
                  border_color = "black",
                  color = viridis(100),
                  cutree_rows = 3,
                  cutree_cols = 3,
                  show_rownames = F,
                  show_colnames = F,
                  filename = "../IntermediaryFiles/pheatmap_prop_viruses_in_common.png",
                  annotation_legend = T)
```

>>>>

pheatmap::pheatmap(prop_high_viruses,
                  annotation_row = ann_row,
                  annotation_col=ann_col,
                  annotation_colors = ann_colors,
                  border_color = "black",
                  color = viridis(100),
                  cutree_rows = 3,
                  cutree_cols = 3,
                  show_rownames = F,
                  show_colnames = F,
                  filename = "../IntermediaryFiles/pheatmap_prop_viruses_in_common.png",
                  annotation_legend = T)

pheatmap::pheatmap(prop_high_viruses,
                  annotation_row = ann_row,
                  annotation_col=ann_col,
                  annotation_colors = ann_colors,
                  border_color = "black",
                  color = c(rep(viridis(3)[1], 5), rep(viridis(3)[2], 4), viridis(3)[3]),
                  cutree_rows = 3,
                  cutree_cols = 3,
                  show_rownames = F,
                  show_colnames = F,
                  filename = "../IntermediaryFiles/pheatmap_prop_viruses_in_common_3_breaks.png",
                  annotation_legend = T)
```
